Supplementary materials

### 2018-08-13 Bibliotemplate.Rmd
mise en page

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphoüet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   
    Understanding the ecological rules underlying the maintenance of tropical forests biodiversity, structure, functioning and dynamics is urgent to anticipate their fate in the global change context.
    The huge diversity of tropical forests is often assumed to be regularly reshaped by natural disturbance yielding a diversity peak at intermediate intensity. This intermediate disturbance hypothesis (IDH), though, remains debated and the controversy questions the extent of communities' resilience regarding their taxonomic and functional facets.

    To disentangle the ecological processes driving community response to disturbance, we analysed the tree community trajectories over 30 years following a disturbance gradient in a Neotropical forest.
    Specifically, we examined community functional and taxonomic trajectories with regards to diversity, composition and redundancy. Functional trajectories were drawn based on 7 leaf, stem and life-history traits.
    We highlighted the cyclic recovery of community taxonomic and functional composition. While pre-disturbance taxonomic differences were maintained over time, functional composition trajectories were quite similar among communities.
    The IDH did predict communities taxonomic diversity response while functional diversity was enhanced whatever the disturbance intensity.
    Although consistent, the recovery of community composition, diversity and redundancy remained unachieved after 30 years. This acknowledged the need of decades-long cycles with no disturbance to ensure a complete recovery, and questioned tropical forest community resilience after repeated disturbances.

keywords: [Taxonomic and Functional Biodiversity, Neotropical Forests, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Long-term Resilience]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

(ref:Bolda) **(a)**

(ref:Boldb) **(b)**

(ref:Boldc) **(c)**

(ref:Boldd) **(d)**

(ref:capThickness) *L_thickness*

(ref:capChloro) *L_chloro*

(ref:capThoughness) *L_toughness*

(ref:capSLA) *SLA*

(ref:capWSG) *WSG*

(ref:capBarkThick) *Bark-thick*

(ref:capHmax) *Hmax*

```{r Options, echo=FALSE, message=FALSE, warning=F}
knitr::opts_chunk$set(cache=F, echo=F,warning=F, tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=40), fig.align="center")
# Installation des packages si nécessaire et chargement
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package, repos="https://cran.rstudio.com/")}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
Library("kableExtra")

## abstract: 204 words / text without legends : 3659 words / references: 68

source("Scripts/DrawingTools.R")
#source("Scripts/GithubPages.R")
```

@@

```{r Tab1, echo=FALSE,as.is=T}
Intervention <- data.frame(
  Treatment=c("Control", "T1", "T2", "T3"),
  Timber=c("", 
           "DBH $\\geq$ 50 cm, commercial species, $\\approx$ 10 trees/ha", 
           "DBH $\\geq$ 50 cm, commercial species, $\\approx$ 10 trees/ha",
           "DBH $\\geq$ 50 cm, commercial species, $\\approx$ 10 trees/ha"),
  Thinning=c("", 
             "", 
             "DBH $\\geq$ 40 cm, non-valuable species, $\\approx$ 30 trees/ha", 
             "DBH $\\geq$ 50 cm, non-valuable species, $\\approx$ 15 trees/ha  "),
  Fuelwood=c("", 
             "", 
             "", 
             "40 cm $\\leq$ DBH $\\leq$ 50 cm, non-valuable species, $\\approx$ 15 trees/ha"),
  AGBLost=c(0, "$[12\\%-33\\%]$", "$[33\\%-56\\%]$", "$[35\\%-56\\%]$")
)
names(Intervention)[5] <- "\\%AGB lost"
knitr::kable(Intervention, caption="Intervention table, summary of the disturbance intensity for the 4 plot treatments in Paracou.", longtable = FALSE, booktabs = TRUE, escape = FALSE,format="latex") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = TRUE)
```

@@

```{r NMDSplans, out.width = '100%', echo=FALSE, fig.cap="Plot trajectories in terms of flora composition (left panels (ref:Bolda) and (ref:Boldc)) and functional composition (right panels (ref:Boldb) and (ref:Boldd)) in a two-dimensional NMDS space. Lower panels ((ref:Boldc) and (ref:Boldd)) represent the euclidean distance to initial condition along the 30 sampled years. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure*"}
load("DB/FunctionalComposition_forGraphs");load("DB/TaxoComposition_forGraphs")
load("DB/FunDistance_ForGraphs");load("DB/TaxoDistance_ForGraphs")

par(mfrow=c(2,2),mar=c(2,2.5,2.5,1),oma=c(1,2,1,3),no.readonly = T)
TaxoCompo(MatrepTaxo)
mtext("Taxonomic composition",side=3,line=1.8,cex=1.05)
FunCompo(MatrepFun)
mtext("Functional composition",side=3,line=1.8,cex=1.05)
EuclidDist(TaxoEuclid)
mtext("Euclidean distance\nfrom 1985 inventory",side=2,padj=0,line=2,cex=0.8)
mtext("(c)",side=3,adj=0,line=0.5)
EuclidDist(FunEuclid)
mtext("(d)",side=3,adj=0,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1,cex=0.8)
legend("right",inset=c(-0.345,0),xpd=NA,legend=c("T0","T1","T2","T3"),col=ColorsTr,lwd=2.5,bty="n",title="Treatment")

```

@@

```{r CWM, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the communities weighted means (CWM) over 30 years after disturbance of 4 leaf traits (Leaf thickness, (ref:capThickness), chlorophyll content, (ref:capChloro), toughness, (ref:capThoughness) and specific area, (ref:capSLA)), 2 stem traits (wood specific gravity, (ref:capWSG), and bark thickness, (ref:capBarkThick)) and one life history trait (Specific maximum height at adult stage, (ref:capHmax)). Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure*"}
load("DB/CWM")

CWMdraw(CWM)
legendCWM()

```

@@

```{r DivTaxo, out.width = '100%', echo=FALSE, fig.cap="Trajectories over 30 years of the difference with the 1989 inventory (2 years after disturbance) of community taxonomic (ref:Bolda) richness, (ref:Boldb), taxonomic evenness, (ref:Boldc) functional richness, and (ref:Boldd) functional evenness. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals ", fig.env="figure*"}
load("DB/ReplacementTraj_ForGraphs")
load("DB/FunctionalTraj_ForGraphs")
load("DB/FunctionalRichnessTraj_ForGraphs")

par(mfrow=c(2,2),mar=c(2,2.5,2.5,1),oma=c(1,2,1,3),no.readonly = T)
TaxoTraj(CompleteTaxo)
plotDiv(CompleteRichFun,remove=TRUE)
mtext("(c) Functional Richness",side=3,adj=0,line=1,cex=0.9)
plotDiv(CompleteFun,remove=TRUE)
mtext("(d) Functional Evenness",side=3,adj=0,line=1,cex=0.9)
mtext("Years since disturbance",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.3,0),xpd=NA,legend=c("T0","T1","T2","T3"),col=ColorsTr,lwd=2.5,bty="n",title="Treatment")

```

@@

```{r IDHplot, out.width = '100%', echo=FALSE, fig.asp = 1.5/4,fig.cap="Relationship between the initial \\%AGB loss and community taxonmic richness (ref:Bolda), taxonomic evenness (ref:Boldb), functional richness (ref:Boldc),and functional evenness (ref:Boldd) at 10, 20 and 30 years after disturbance", fig.env="figure*"}
load("DB/RichnessIDH");load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB");load("DB/FunRichIDH")

par(mfrow=c(1,4),mar=c(2,2.5,3,1),oma=c(1,1,1,2.5),no.readonly=TRUE)
plotIDH(Data=Rich,AgbLoss=AGBloss)
mtext("(a) Taxonomic\nRichness",line=1,side=3,adj=0,cex=0.85)
mtext("Equivalent diversity",side=2,line=2.2,adj=1,cex=0.8)
plotIDH(Data=Sim,AgbLoss=AGBloss)
mtext("(b) Taxonomic\nEvenness",line=1,side=3,adj=0,cex=0.85)
plotIDH(Data=Rao,AgbLoss=AGBloss)
mtext("(c) Functional\nRichness",line=1,side=3,adj=0,cex=0.85)
plotIDH(Data=FunRich,AgbLoss=AGBloss)
mtext("(d) Functional\nEvenness",line=1,side=3,adj=0,cex=0.85)
mtext("initial AGB loss (%)",side=1,line=2.2,adj=1,cex=0.8)
legend("right",inset=c(-0.5,0),xpd=NA,legend=c("10","20","30"),col=colyear,lwd=2.5,bty="n",title="Years")

```

@@

```{r RedFunRest, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy within the initial functional space over 30 years after disturbance. Colors are disturbance treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure"}
load("DB/Redundancy_restricted")

par(mar=c(3,2,3,2))
RedundancyPlot(RedundancyTraj_restricted)
mtext("Functional Redundancy",side=3,adj=0,line=1.5,cex=1.5)
mtext("Restricted to initial functional space",side=3,adj=0,cex=1.2,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1,cex=1.5)

```

@@

`r if (knitr:::is_html_output()) '# References {-}'`

>>>>

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"

bibliography      : [references.bib]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_word
---

```{r load_packages, include = FALSE}
library("papaja")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```

@@

@@

@@

@@

@@

@@

@@

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
